### 2023-01-24 Poisot_et_al_2023_ncbitaxonomyjl__draft.tex
Deploying to gh-pages from @ PoisotLab/ms_ncbitaxonomy_softwarenote@5b8bfd89b09323b98fb36465b3c4d98c36fa1b45 🚀

An up-to-date version of the documentation for \texttt{NCBITaxonomy.jl}
can be found online from the EcoJulia documentation hub
\href{https://docs.ecojulia.org/NCBITaxonomy.jl/stable/}{https://docs.ecojulia.org/},
including examples and in-line documentation of every method. The
package is released under the MIT license. Contributions can be made in
the form of issues (bug reports, questions, features suggestions) and
pull requests.

In order to achieve good performance, the package will first retrieve
the latest (as validated by its checksum) NCBI taxonomy backbone, store
it locally, and pre-process it as a set of Julia data tables. By
default, the taxonomy will be downloaded to the Julia package
repository, which is not an ideal solution, and therefore we recommend
that users set an environment variable to specificy where the data will
be loaded from (this path will be created if it doesn't exist):

@@

Note that this location can be different for different projects, as the
package is able to update the taxoonmic backbone (and will indeed prompt
the user to do so if the taxonomy is more than 90 days old). The package
can then be checked out and installed anonymously from the central Julia
repository:

@@

This software note describes version \texttt{v0.2.3} of the package (we
follow semantic versioning), which works on Julia 1.5 upwards. The
dependencies are all resolved by the package manager at installation,
and (on the user-facing side) include the \texttt{StringDistances.jl}
package, allowing users to experiment with different string matching
methods. As is best practices for Julia packages, a
\texttt{Project.toml} file specifying compatible dependencies versions
is distributed with the package. The code is covered by unit-tests (with
about 98\% coverage), as well as integration tests as part of the
documentation (specifically, a use-case detailing how to clean data from
a biodiversity survey, and a use-case aiming to reconstruct a taxonomic
tree for the Lemuriformes).

>>>>

An up-to-date version of the documentation for \texttt{NCBITaxonomy.jl}
can be found in the package \texttt{git} repository
(\url{https://github.com/PoisotLab/NCBITaxonomy.jl}), including examples
and in-line documentation of every method. The package is released under
the MIT license. Contributions can be made in the form of issues (bug
reports, questions, features suggestions) and pull requests.

In order to achieve good performance, the package will first retrieve
the latest (as validated by its checksum) NCBI taxonomy backbone, store
it locally, and pre-process it as a set of Julia data tables. By
default, the taxonomy will be downloaded to the user's hoome directory,
which is not an ideal solution, and therefore we recommend that users
set an environment variable to specificy where the data will be loaded
from (this path will be created if it doesn't exist):

@@

Note that this location can be different for different projects, as the
package is able to update the taxonomic backbone (and will indeed prompt
the user to do so if the taxonomy is more than 90 days old). The package
can then be checked out and installed anonymously from the central Julia
repository:

@@

This software note describes version \texttt{v0.3.0} of the package (we
follow semantic versioning), which works on Julia 1.5 upwards. The
dependencies are all resolved by the package manager at installation,
and (on the user-facing side) include the \texttt{StringDistances.jl}
package, allowing users to experiment with different string matching
methods. As is best practices for Julia packages, a
\texttt{Project.toml} file specifying compatible dependencies versions
is distributed with the package. The code is covered by unit-tests (with
about 98\% coverage), as well as integration tests as part of the
documentation (specifically, a use-case detailing how to clean data from
a biodiversity survey, and a use-case aiming to reconstruct a taxonomic
tree for the Lemuriformes).
